Precision calculations of cosmic shear projections

### 2017-02-10 limber2.tex
Figures updates labels

To further develop equation~(\ref{eq:P_geom_mean}), we divide out the growth factor to
define a redshift-independent power spectrum $P_{\rm m}(k)$,
%
\begin{equation}
 P_{\rm m}(k, \chi) =: D_+(\chi) P_{\rm m}(k).
  \label{eq:P_k_chi_sep_s}
\end{equation}
%
This is not exact, since some non-linear prescriptions of the power spectrum
depend on redshift other than the growth factor, for example when computing the
non-linear scale $k_{\rm NL}(z)$ for \texttt{halofit}.

With this approximation, the \mk{$\chi$-independent term $P_{\rm m}(k)$}
factors out from equation~(\ref{eq:f_LA08}), and we define the separated kernel
function $f_{\rm s}$ as
%
\begin{equation}
  f_{\rm s}(\chi) = D_+(\chi) a^{-1}(\chi) \chi^{-3/2} q(\chi) \,
  \label{eq:f_LA08_s}
\end{equation}
%
The second-order Limber term of the shear power spectrum can then be simplified to
%
\begin{align}
  C^\gamma_{{\rm L2}, ij}(\ell) = & - \frac 1 {\nu^2} \, \frac{\ellbar^2(\ell, 2)}{\nu^4} \, \pref^2
    \int {\rm d} \chi \, \chi^{2} a^{-2} P_{\rm m}\left(\frac\nu\chi; \chi\right)
    %\nonumber \\
    %& \times
    \frac {a(\chi)}{2 D_+(\chi)} \chi^{3/2}
    \left[ q^{}_i f^{\prime\prime}_{{\rm s} j} + f^{\prime\prime}_{{\rm s}i} q^{}_j
      + \frac{\chi}{3} \left( q^{}_i f^{\prime\prime\prime}_{{\rm s}j} + f^{\prime\prime\prime}_{{\rm s}i} q^{}_j
      \right)
    \right](\chi)
  \label{eq:C_ell_limber2_dr_s}
\end{align}
%
We compute the numerical higher derivatives as follows. The functions $f_{\rm
s}(\chi)$ are fit as power laws with index $\approx 1.5$. The fit is
performed between $\chi_{\rm min} = 0.001 {\rm Mpc}/h$ and $\chi_{\rm max} =
500 \mbox{Mpc}/h$. At larger comoving distances the kernel decreases faster
than a power law, so we exclude this range from the fit. Even though the
derivaties are larger due to the steeper decline, the associated errors are
very small as these scales are down-weighed by the kernel function $f_{\rm
s}$ itself. At $\chi = 500 \mbox{Mpc}/h$ the filter function is less than
$10^{-4}$ of its value of unity at 1\,Mpc$/h$. \textbf{PLEASE CHECK!}

@@

  \begin{center}
    \resizebox{1.0\hsize}{!}{
      \includegraphics{figures/P_kappa_limber_comp}
      \includegraphics{figures/P_kappa_limber_delta}
    }
  \end{center}

@@

As we have shown in section~\ref{sec:comp}, however, the spherical
second-order extended Limber approximation provides a percent-level precision
representation of the full spherical projection for $\ell > 3$.  
In the Limber approximations the Bessel functions \mk{are expanded into}
polynomials, allowing for arbitrary wave modes $\ell$. The spherical pre-factor
$\ellbar(\ell, 2)$ (equation~\ref{eq:ellbar}) can be generalised to non-integer
arguments and is positive for $\ell \le 2$. We can thus use the spherical power
spectrum in the Limber approximations for the Hankel transformation to compute
the two-point correlation functions.  We therefore do not
present predictions for the two-point shear correlation function using the full
spherical projection, instead choosing the spherical second-order extended
Limber approximation (ExtL2Sph) \textbf{PLEASE CHECK!} as our reference in this case.

@@

The authors thank Tommaso Giannantonio, Sarah Bridle, Ami Choi, Donnacha Kirk, Lance Miller, Benjamin Joachimi, Chris Blake and Adam Amara for very helpful discussions.
This work was financially supported by the DFG (Emmy Noether grants Hi 1495/2-1 and SI 1769/1-1; TR33 `The Dark Universe'), the Alexander von Humboldt Foundation, the ERC (grants 279396, 647112), the Seventh Framework Programme of the European Commission (Marie Sklodwoska Curie Fellowship grant 656869), NSERC and CIfAR.

>>>>

To further develop equation~(\ref{eq:P_geom_mean}), we divide out the growth factor to
define a redshift-independent power spectrum $P_{\rm m}(k)$,
%
\begin{equation}
 P_{\rm m}(k, \chi) =: D_+(\chi) P_{\rm m}(k).
  \label{eq:P_k_chi_sep_s}
\end{equation}
%
This is not exact, since some non-linear prescriptions of the power spectrum
depend on redshift other than the growth factor, for example when computing the
non-linear scale $k_{\rm NL}(z)$ for \texttt{halofit} \citep{2003MNRAS.341.1311S}.

With this approximation, the \mk{$\chi$-independent term $P_{\rm m}(k)$}
factors out from equation~(\ref{eq:f_LA08}), and we define the separated kernel
function $f_{\rm s}$ as
%
\begin{equation}
  f_{\rm s}(\chi) = D_+(\chi) a^{-1}(\chi) \chi^{-3/2} q(\chi) \,
  \label{eq:f_LA08_s}
\end{equation}
%
The second-order Limber term of the shear power spectrum can then be simplified to
%
\begin{align}
  C^\gamma_{{\rm L2}, ij}(\ell) = & - \frac 1 {\nu^2} \, \frac{\ellbar^2(\ell, 2)}{\nu^4} \, \pref^2
    \int {\rm d} \chi \, \chi^{2} a^{-2} P_{\rm m}\left(\frac\nu\chi; \chi\right)
    %\nonumber \\
    %& \times
    \frac {a(\chi)}{2 D_+(\chi)} \chi^{3/2}
    \left[ q^{}_i f^{\prime\prime}_{{\rm s} j} + f^{\prime\prime}_{{\rm s}i} q^{}_j
      + \frac{\chi}{3} \left( q^{}_i f^{\prime\prime\prime}_{{\rm s}j} + f^{\prime\prime\prime}_{{\rm s}i} q^{}_j
      \right)
    \right](\chi)
  \label{eq:C_ell_limber2_dr_s}
\end{align}
%
We compute the numerical higher derivatives as follows. The functions $f_{\rm
s}(\chi)$ are fit as power laws with index $\approx 1.5$. The fit is
performed between $\chi_{\rm min} = 0.001 {\rm Mpc}/h$ and $\chi_{\rm max} =
500 \mbox{Mpc}/h$. At larger comoving distances the kernel decreases faster
than a power law, so we exclude this range from the fit. Even though the
derivaties are larger due to the steeper decline, the associated errors are
very small as these scales are down-weighed by the kernel function $f_{\rm
s}$ itself. At $\chi = 500 \, \mbox{Mpc}/h$ the filter function is less than
$10^{-4}$ of its value of unity at $1$\,Mpc$/h$.

@@

  \begin{center}
    \resizebox{1.0\hsize}{!}{
      \includegraphics{figures/P_kappa_limber_comp}
      \hspace*{2em}
      \includegraphics{figures/P_kappa_limber_delta}
    }
  \end{center}

@@

As we have shown in section~\ref{sec:comp}, however, the spherical
second-order extended Limber approximation provides a percent-level precision
representation of the full spherical projection for $\ell > 3$.  
In the Limber approximations the Bessel functions \mk{are expanded into}
polynomials, allowing for arbitrary wave modes $\ell$. The spherical pre-factor
$\ellbar(\ell, 2)$ (equation~\ref{eq:ellbar}) can be generalised to non-integer
arguments and is positive for $\ell \le 2$. We can thus use the spherical power
spectrum in the Limber approximations for the Hankel transformation to compute
the two-point correlation functions.  We therefore do not
present predictions for the two-point shear correlation function using the full
spherical projection, instead choosing the spherical second-order extended
Limber approximation (ExtL2Sph) as our reference in this case.

@@

The authors thank Tommaso Giannantonio, Sarah Bridle, Ami Choi, Donnacha Kirk,
Lance Miller, Benjamin Joachimi, Chris Blake and Adam Amara for very helpful
discussions. This work was financially supported by the DFG (Emmy Noether
grant Hi 1495/2-1; SI 1769/1-1; TR33 `The Dark Universe'), the Alexander
von Humboldt Foundation, the ERC (grants 279396, 647112), the Seventh Framework
Programme of the European Commission (Marie Sklodwoska Curie Fellowship grant
656869), NSERC and CIfAR.
